
\begin{cnabstract}
本文介绍了我实现的一个幼儿教育领域应用从需求调研到产品设计，到最后实现的流程和部分细节。在第一章绪论中， 介绍了该应用的应用场景也就是： 幼儿园老师和家长之间交互，幼儿园管理层对于老师的有效管理，家长对于自己孩子生活点滴的记录，家长之间针对孩子的社交。  之后在第二章相关技术介绍中， 对实现该产品的相关技术 Nodejs, Mongodb, Angularjs做了简要介绍。 在第三章系统需求分析中， 详细而且细粒度地说明了用户到底需要哪些具体的功能， 并给出了工作流图。 在第四章系统概要设计中，给出了该系统的代码设计架构和数据库设计出发点。  在第五章系统详细设计与实现中， 给出了具体Nosql数据库结构化的数据定义和代码设计中各个模块的功能和部分实现细节。 在第六章中，介绍了系统测试的内容和步骤。 最后第七章总结了该系统的意义， 和未来的工作计划。

\keywords{网络后端开发，数据库设计，移动开发，需求调研，界面设计，网络前端开发，NoSQL}
\end{cnabstract}


\begin{enabstract}

This paper introduce the development of an application for areas of early childhood education, including NeedFinding, BenchMarking, Product Design, Implementation, Testing, Future Plan.  In the first chapter, it explains the application scenarios: interaction between teachers and parents, management of teachers and classes, life records on children from parents, social networking between parents based on children.  In the second chapter, it introduce technologies like Nodejs, Mongodb, Angularjs that used in this application. In the third chapter, it introduces the users' need, what functions they want and workflow chart.  In the fourth chapter, it gives the code design structure and database design. In the fifth chapter, it provides the details of the database schema and the api interfaces and implementation details for each module in this application. In the sixth chapter,  it introduces the testing procedure of this system. In the seventh chapter, it gives a brief summary of the significance
of this application and future plan.

\enkeywords{Web Backend Development, DataBase Design, Mobile Development, NeedFinding, Interface Design, Web Frontend Development, NoSQL}
\end{enabstract}
